---
title: "Googling Depression and Anxiety as terms to describe one's experience." 
author: Thomas Tsichtis, Ismini Lymtsiouli, Maria Batzaki
bibliography: Style/s.bib 
csl: Style/apa.csl 
output: ioslides_presentation 
widescreen: TRUE

---
```{r cache=FALSE, include=FALSE}
knitr::read_chunk('data_collection.R')
```

```{r include=FALSE}

library("gtrendsR")

trends<-gtrends(keyword =c("anxiety","depression"), geo=("GR"),time=("2018-01-01 2018-12-31"))

trends


interest_over_time<-trends$interest_over_time
interest_over_time


write.csv(interest_over_time,file="interest_over_time")


group_a<-interest_over_time$keyword
group_b<-interest_over_time$hits

 
df_wide<-data.frame(group_a,group_b)
anxiety_name<-group_a[1:52]
anxiety_hits<-group_b[1:52]
Anxiety<-cbind(anxiety_name,anxiety_hits)
depression_name<-group_a[53:104]
depression_hits<-group_b[53:104]
Depression<-cbind(depression_name,depression_hits)

cor.test(anxiety_hits,depression_hits)
result <- cor.test(anxiety_hits,depression_hits)
str(result)
names(result)


plot(anxiety_hits~depression_hits,col=30,main = "Correlation between searches on Anxiety and Depression", cex=1.5, cex.main=1, font.main=4, font.lab=2, font.axis=3, xlab="Anxiety", ylab="Depression", pch=20)

```


## Introduction

Psychiatric and Psychological terms describing mental health issues have been a contested topic.

What is the relationship between depression and anxiety?

According to the DSM-5  [@association_diagnostic_2013]:   

Depressive Disorders are...

Anxiety Disorders are...

## 

_Validity issues concerning:_

Comorbidity [@kring_abnormal_2012]

Individual experience and meaningfulness [@cromby_psychology_2013]

How does the wider population describe these states?

Complex but common sense, internet and easy access?

## Method

Indicators of searching what I am observing using specific expert-borrowed descriptive labels?

and then googling it?

Google Trends.

Depression and Anxiety as search terms.

Covary consistently?

_Hypothesis: Depresion and Anxiety covary as search terms on google._

## Results and Graphics
Pearson's R product-moment correlation showed a weak unimportant relationship ( _r_= `r round(result$estimate, 2)`, _p_=`r round (result$p.value, 2)`).

```{r echo=FALSE}
plot(anxiety_hits~depression_hits,col=30,main = "Correlation between searches on Anxiety and Depression", cex=1.5, cex.main=1, font.main=4, font.lab=2, font.axis=3, xlab="Anxiety", ylab="Depression", pch=20)
```



## Discussion

Assumptions and simplicity.

Searching google is probably more complex.

Not a simple a-theoretical, common-sensical relationship.

## Referecnces
